Atomify - a live LAMMPS visualizer

### 2016-05-23 ms.tex
Added pipeline

>>>>

\subsubsection*{Pipeline}
When rendering one often wants to modify the data from LAMMPS before it is visualized. Examples are periodic images of the simulation, slicing and coloring. We have been inspired by the pipeline used in Ovito where the data flows through several \textit{modifiers}, each modifying the visualization data before the data is converted to a format for the GPU.
